A Multi-Scale Analysis of 27,000 Urban Street Networks\footnote{This is a journal article manuscript currently under peer review.}

### 2017-03-21 latex/paper.tex
update cite style

\documentclass[Afour,sageh,times]{sage/sagej}

\usepackage{moreverb,url}
\usepackage{csvsimple}
\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}

\bibliographystyle{plainnat}
\setcitestyle{numbers}

\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\def\volumeyear{2017}
\begin{document}
\runninghead{Boeing}
\title{A Multi-Scale Analysis of 27,000 Urban Street Networks}
\author{Geoff Boeing\affilnum{1}}
\affiliation{\affilnum{1}PhD Candidate, Department of City and Regional Planning, University of California, Berkeley}
\corrauth{Geoff Boeing,
Department of City and Regional Planning,
University of California, Berkeley,
United States}
\email{gboeing@berkeley.edu}

\begin{abstract}
This paper serves illustrative purposes as it presents wide-ranging preliminary empirical findings on US urban form and street network characteristics, using OSMnx. It also demonstrates the scalability and flexibility of OSMnx as a new research tool. This paper addresses past limitations by conducting an analysis of street networks with large sample sizes, with clearly defined network definitions and extents for reproducibility, and using non-planar, directed graphs. In particular, it examines urban street networks focusing on structure, connectedness, centrality, and robustness. In total it cross-sectionally analyzes 497 urbanized areas' street networks, 19,655 cities' and towns' street networks, and 6,857 neighborhoods' street networks. These sample sizes are larger than those in any previous study and the preliminary empirical findings illustrate the use of OSMnx as a new research platform.
\end{abstract}

\keywords{network analysis, street network, urban design, urban form, urban planning}

\maketitle

@@

\begin{table*}[h]
\caption{Central tendency and statistical dispersion for selected measures of all US urbanized areas' street networks.}
\label{table01}
\csvautotabular{media/table01.csv}
\end{table*}

@@

\begin{figure}[h]
\includegraphics[width=0.45\textwidth]{media/fig02.png}
\caption{Distribution of node types in 9 urbanized areas, with number of streets emanating from the node on the \emph{x}-axis and proportion of nodes of this type on the \emph{y}-axis }
\label{fig02}
\end{figure}

@@

\begin{table*}[h]
\caption{Selected measures of the 30 largest (by land area) urbanized areas' street networks.}
\label{table02}
\csvautotabular{media/table02.csv}
\end{table*}

@@

\begin{table*}[h]
\caption{Selected summary stats for every incorporated city and town in the US.}
\label{table03}
\csvautotabular{media/table03.csv}
\end{table*}

\begin{figure}[h]
	\includegraphics[width=0.45\textwidth]{media/fig03-v.png}
	\caption{The linear relationship between total street length and number of nodes in the street networks of 6,857 US neighborhoods (top) and 19,655 US cities and towns (bottom).}
	\label{fig03}
\end{figure}

@@

\begin{table*}[h]
\caption{Median values, aggregated by state plus DC, of selected measures of the municipal-scale street networks for every city and town in the US.}
\label{table04}
\csvautotabular{media/table04.csv}
\end{table*}

@@

\begin{table*}[h]
\caption{Selected summary stats for all the neighborhood-scale street networks.}
\label{table05}
\csvautotabular{media/table05.csv}
\end{table*}

@@

\begin{figure*}[h]
	\includegraphics[width=1\textwidth]{media/fig05.png}
	\caption{Square-mile comparisons of central cities and their suburbs. Left: top, downtown Philadelphia; bottom, its suburb, King of Prussia. Middle: top, downtown Portland; bottom, its suburb, Beaverton. Right: top, downtown San Francisco; bottom, its suburb Concord.}
	\label{fig05}
\end{figure*}

@@

\begin{acks}
Redacted
\end{acks}

>>>>

\documentclass{article}

\usepackage{graphicx}
\usepackage{csvsimple}
\usepackage[numbers]{natbib}
\usepackage[affil-it]{authblk}

\bibliographystyle{apalike}

\begin{document}
\title{A Multi-Scale Analysis of 27,000 Urban Street Networks\footnote{This is a journal article manuscript currently under peer review.}}
\author{Geoff Boeing\footnote{Email address: gboeing@berkeley.edu; corresponding author.}}
\affil{Department of City and Regional Planning\\University of California, Berkeley}
\date{\today}
\maketitle

\begin{abstract}
OpenStreetMap presents an emerging source of worldwide geospatial urban data useful to researchers. This paper uses the OSMnx software to automatically download and analyze 27,000 street networks from OpenStreetMap at metropolitan, municipal, and neighborhood scales---that is, every urbanized area, incorporated place, and Zillow neighborhood in the US. In turn it presents wide-ranging empirical findings on US urban form and street network characteristics. This paper addresses past limitations by conducting an analysis of street networks with an extremely large sample sizes, with clearly defined network definitions and extents for reproducibility, and using non-planar, directed graphs. Its analysis emphasizes urban street networks measures relevant to urban design and morphology, including structure, connectedness, centrality, and robustness. In total we cross-sectionally analyze the street networks of 497 urbanized areas, 19,655 cities and towns, and 6,857 neighborhoods. These sample sizes are larger than those in any previous study and illustrate the use of OSMnx and OpenStreetMap as a new urban form research platform.
\end{abstract}

@@

\begin{table*}[hp]
\caption{Central tendency and statistical dispersion for selected measures of all US urbanized areas' street networks.}
\label{table01}
\csvautotabular{media/table01.csv}
\end{table*}

@@

\begin{figure*}[hp]
\includegraphics[width=1\textwidth]{media/fig02.png}
\caption{Distribution of node types in 9 urbanized areas, with number of streets emanating from the node on the $x$-axis and proportion of nodes of this type on the $y$-axis }
\label{fig02}
\end{figure*}

@@

\begin{table*}[hp]
\caption{Selected measures of the 30 largest (by land area) urbanized areas' street networks.}
\label{table02}
\csvautotabular{media/table02.csv}
\end{table*}

@@

\begin{table*}[hp]
\caption{Selected summary stats for every incorporated city and town in the US.}
\label{table03}
\csvautotabular{media/table03.csv}
\end{table*}

\begin{figure*}[h]
	\includegraphics[width=1\textwidth]{media/fig03.png}
	\caption{The linear relationship between total street length and number of nodes in the street networks of 6,857 US neighborhoods (top) and 19,655 US cities and towns (bottom).}
	\label{fig03}
\end{figure*}

@@

\begin{table*}[hp]
\caption{Median values, aggregated by state plus DC, of selected measures of the municipal-scale street networks for every city and town in the US.}
\label{table04}
\csvautotabular{media/table04.csv}
\end{table*}

@@

\begin{table*}[hp]
\caption{Selected summary stats for all the neighborhood-scale street networks.}
\label{table05}
\csvautotabular{media/table05.csv}
\end{table*}

@@

\begin{figure*}[h]
	\includegraphics[width=1\textwidth]{media/fig05.png}
	\caption{Square-mile comparisons of central cities and their suburbs. Left: top, downtown Philadelphia; bottom, its suburb, King of Prussia. Middle: top, downtown Portland; bottom, its suburb, Beaverton. Right: top, downtown San Francisco; bottom, its suburb, Concord.}
	\label{fig05}
\end{figure*}

@@
